Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-12 papers/ms.tex
update ms

The discovery and characterization of transiting planets younger than
a billion years is a major frontier in current exoplanet research.
The reason is that the properties of young planets provide benchmarks
for studies of planetary evolution.  For instance, young planets can
help inform our understanding
of when hot Jupiters arrive on their close-in orbits
\citep{dawson_johnson_2018}, how the sizes of planets with massive
gaseous envelopes evolve \citep{rizzuto_tess_2020}, when and if
close-in multiplanet systems fall out of resonance
\citep{arevalo_stability_2022,goldberg_architectures_2022}, and
whether and how mass-loss explains the radius valley
\citep{lopez_how_2012,Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018,lee_primordial_2021}.

The discovery of a young planet requires two claims to be fulfilled:
the planet must exist, and its age must be secured.  Spaced-based
photometry from K2 and TESS has yielded a number of exemplars for
which the planetary evidence comes from transits, and the age is based
on either cluster membership
\citep{Mann_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,nardiello_pathosII_2020}
or else on correlates of youth such as stellar rotation, photospheric
lithium content, x-ray activity, or emission line strength
\citep{zhou_2021_tois,hedges_toi-2076_2021}.

In this work, we leverage recent analyses of the Gaia data, which have
greatly expanded our knowledge of stellar groups \citep[{\it
e.g.},][]{CantatGaudin2018a,KounkelCovey2019,Kerr2021}.  To date these
analyses have mostly clustered on the stellar positions and 2-D
velocities.  One important result is the discovery of
diffuse streams and tidal tails comparable in stellar mass to the
previously known cores of nearby open clusters
\citep{meingast_psceri_2019,Meingast2021,gagne_number_2021}.  Even
though these streams are spread over tens to hundreds of
parsecs, their velocity dispersions can remain coherent at the
$\sim$1\kms\ level.  They can also be much larger: as an extreme
example, internal dynamics and projection effects in the Hyades drive
stars in the tidal tails to $\pm 40\mkms$ in relative velocity
when projected against the cluster center \citep{jerabkova_800_2021}.
The stars in such diffuse regions can be verified to be the same age
as the core members ({\it i.e.}, coeval) through analyses of
color-absolute magnitude diagrams \citep{KounkelCovey2019}, stellar
rotation periods \citep{curtis_tess_2019,bouma_2021_ngc2516}, and
chemical abundances \citep{hawkins_2020}.  While there are 
implications for our understanding of star formation and cluster
evolution \citep{dinnbier_tidal_2020}, a separate consequence is that
we now know the ages of many more stars, including previously known
planet hosts.

@@

In this work, we expand on our earlier study of a $38^{+7}_{-6}$ Myr
old Neptune-sized planet in the Kepler field (Kepler-1627~Ab;
\citealt{bouma_kep1627_2022}).  The age of this planet was derived
based on its host star's membership in the $\delta$\ Lyr\ cluster.
Our analysis of the cluster focused on the immediate vicinity of
Kepler-1627 in order to secure the planet's age.  However it became
clear that the $\delta$\ Lyr\ cluster seems to
also be part of a much larger group of similarly aged stars.  This
group, which is at a distance of $\sim$330\,pc from the Sun, 
spans Cepheus to Hercules (galactic longitudes, $l$, between
40$^\circ$ and 100$^\circ$), at galactic latitudes roughly between
0$^\circ$ and 20$^\circ$.  We therefore refer to it as the Cep-Her
complex.  It exhibits significant sub-structure over its $\approx$250
parsec length, and a detailed analysis of its memberships, kinematics,
and possible origin is currently being prepared by R.~Kerr and
collaborators.

Here, our focus is on the intersection of the Cep-Her complex with the
Kepler field.  Cross-matching our Cep-Her members against known Kepler
Objects of Interest (KOIs; \citealt{thompson_planetary_2018}) yielded
four candidate cluster members: Kepler-1627, Kepler-1643, KOI-7368,
and KOI-7913.  Given our earlier analysis of Kepler-1627, we focus
here on the latter three.  After analyzing the relevant properties of
Cep-Her (Section~\ref{sec:cluster}), we derive the stellar properties
(Section~\ref{sec:stars}) and validate the planetary nature of each
system using a combination of the Kepler photometry and
high-resolution imaging (Section~\ref{sec:planets}).  We conclude with
a discussion of mini-Neptune size evolution, and point out possible
directions of future work (Section~\ref{sec:disc_conc}).

@@

Our focus is on a region of the Galaxy approximately 200 to 500\,pc
from the Sun, above the galactic plane, and spanning galactic
longitudes of roughly $40^\circ$ to $100^\circ$ degrees.  Two rich
clusters in this region are the $\delta$~Lyra cluster
\citep{stephenson_possible_1959} and RSG-5 \citep{roser_nine_2016}.
Each of these clusters was known before Gaia.  They have reported ages
between 30 and 60\,Myr.  Early empirical
evidence that these two clusters could be part of a large and more
diffuse population was apparent in the Gaia-based photometric analysis
of pre-main-sequence stars by \citet[][see their Figures~11
and~13]{Zari2018}.  Further kinematic connections and complexity were
highlighted by \citet{KounkelCovey2019}, who included these previously
known groups in the larger structures dubbed ``Theia~73'' and
``Theia~96''\footnote{See their visualization online at
\url{http://mkounkel.com/mw3d/mw2d.html} (accessed 15 March 2022)}.
The connection made by \citet{KounkelCovey2019} between the previously
known open clusters and the other groups in the region was made as
part of an unsupervised clustering analysis of the Gaia DR2 positions
and tangential velocities with a subsequent manual ``stitching'' step.
Their results support the idea that there is an overdensity of
30 to 60\,Myr old stars in this region of
the Galaxy.  \citet{Kerr2021}, in a volume-limited analysis of the
Gaia DR2 point-source catalog out to one third of a kiloparsec,
identified three of the nearest sub-populations, dubbed
``Cepheus-Cygnus'', ``Lyra'', and ``Cerberus''.  \citet{Kerr2021}
reported ages for each of these subgroups between 30 and 35 Myr.

@@

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric, defined
such that the group member with the smallest core distance has a
weight of 1, the group member with the greatest core distance has a
weight of 0, and weights for the other group members are log-normally
distributed between these two extremes.  In Figure~\ref{fig:XYZvtang},
we show 12{,}436 objects with weight exceeding 0.02 as gray points,
and overplot 4{,}763 objects with weights exceeding 0.10 as black
points.\footnote{These counts only include objects with reliable
astrometry and photometry: $\varpi/\sigma_\varpi>5$;
$G/\sigma_{G}>50$; $G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm
BP}/\sigma_{G_{BP}}>20$.} The previously known $\delta$~Lyr\ cluster
is visible at $(l,b)=(68^\circ,15^\circ$) and $(v_{l'}, v_b)=(-4.5
\mkms,-4 \mkms)$.  RSG-5 is visible at $(l,b)=(83^\circ,6^\circ)$,
$(v_{l'}, v_b)=(5.5 \mkms,-3.5 \mkms)$.  Most of the other
subclusters, including in Cep-Cyg ($l,b=90^\circ,7^\circ$) and
Cerberus ($l,b=48^\circ,18^\circ$) are too small or dispersed to have
previously been analyzed in great detail.

@@

\paragraph{Cep-Her}
Our analysis to date has focused only on portions of Cep-Her
that were observed by Kepler: namely RSG-5, CH-2, and the $\delta$~Lyr
cluster.
The membership and kinematics of the other components shown 
in Figure~\ref{fig:XYZvtang} also deserve attention.
R.~Kerr and collaborators have acquired
{\bf N spectra} from which radial velocities will be derived in their upcoming study, but if the estimate that
Cep-Her has $\approx$3{,}500 stars is correct then far more might be required
to fully untangle the kinematics of the various groups.
Wide-field spectroscopic surveys such as LAMOST ({\bf cite}) or
APOGEE ({\bf cite}) could provide sensitivity to the Li 6708\,\AA\ line,
which would enable a more detailed analysis of its abundance across
FGK stars.
Gaia DR3 may also provide RVS spectra
for some of the brighter F and G dwarfs, which could provide the calcium
infrared triplet as another age indicator.

A number of worthy photometric projects also seem possible
given the new understanding of the complex.
One is asteroseismology of the $\delta$~Sct stars,
using either TESS or Kepler data.
For cases in which the modes are resolved, this might yield
age estimates for subgroups independent from other
approaches.
Other projects could include searches of the Kepler data
for exocomets (CITE Zieba), or for missed planets around the
most rapid rotators.

\paragraph{Exoplanet demographics at early times}
Our main motivation for finding new young planets is to help
benchmark models for planetary evolution.
However demographic analyses of the known planets between $10^7$ and $10^9$ years
(Figure~\ref{fig:age}) have so far been somewhat limited.
Approximately 40 such planets
are now known.
The majority of published cases ($\approx$20) come from
K2, though now $\approx$10 come from Kepler, and $\approx$10 
from TESS.

Given these detections, 
a few reflections regarding the experimental design of any
demographic survey might be helpful.
The first is that the list of target stars is an incredibly important
ingredient, and the best way to compile relevant stars right
now is likely through a combination of automated spatio-kinematic clustering
from Gaia and rotation-period measurement with TESS.
The second is that the planets $<$$3$\,$R_\oplus$ in size
all come from either K2 or Kepler.
So demographic inferences based on TESS
for the time being are limited to 
$4$ to $10$\,$R_\oplus$, close-in to the host stars.  
It seems worthwhile to comparable
the absolute occurrence rate of such planets to those derived from
Kepler (CITE Petigura).
One question that seems like it should be within reach would be to clarify
whether enough young stars have been searched for the dearth of
young hot Jupiters shown in Figure~\ref{fig:age} to be significant.
Since the hot Jupiter occurrence rate is strongly dependent on stellar
mass and metallicity (CITE), particular care would be needed to select
a sample of FGK dwarfs for the measurement, likely going out
to distances of $\approx$500\,pc to get enough stars.
The major sources of stars in the youngest age bins would
need to include Sco OB2, Cep-Her, and Orion, among others.
For studies of how mini-Neptune sizes evolve, the combined K2 and Kepler
dataset might be the better primary source.
Though the selection function is more stringent, for a given star
Kepler acquired $\sim$100$\times$ more photons.  Given the
star-count limited nature of a cluster-based exoplanet demographic
survey, every star counts.

@@

%\clearpage
\acknowledgements
\raggedbottom
%
L.G.B{.} acknowledges support from the TESS GI Program (NASA grants
80NSSC19K0386 and 80NSSC19K1728) and the Heising-Simons Foundation (51 Pegasi~b
Fellowship).
% programs G011103 and G022117, through 
%
%
%FIXME
Keck/NIRC2 imaging was acquired by program 2015A/N301N2L
(PI: A.~Kraus). % and 2019A/N069 (PI: E.~Petigura).
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
This paper also includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham,
S.~Seager, J.~Jenkins) and the many TESS team members for their
efforts to make the mission a continued success.
%
%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
%Finally, this research has made use of the Keck Observatory Archive (KOA),
%which is operated by the W. M. Keck Observatory and the NASA Exoplanet
%Science Institute (NExScI), under contract with the National
%Aeronautics and Space Administration.
Finally, we also thank the Keck Observatory staff for their support of
HIRES and remote observing.  We recognize the importance that the
summit of Maunakea has within the indigenous Hawaiian community, and
are deeply grateful to have the opportunity to conduct observations
from this mountain.
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%

@@

\clearpage
\bibliographystyle{yahapj}                            
\bibliography{bibliography}

@@

Tables~\ref{tab:kepler1643}, \ref{tab:koi7368}, \ref{tab:koi7913} give
the full set of fitted and derived parameters from the model described in
Section~\ref{sec:fitting}.
Priors and convergence statistics are also listed.

@@

\input{source_Kepler_1643_simpletransit_posteriortable.tex}
\input{source_KOI_7368_simpletransit_posteriortable.tex}
\input{source_KOI_7913_simpletransit_posteriortable.tex}

>>>>

The discovery and characterization of planets younger than
a billion years is a major frontier in current exoplanet research.
The reason is that the properties of young planets provide benchmarks
for studies of planetary evolution.  For instance, young planets can
inform our understanding
of when hot Jupiters arrive on their close-in orbits
\citep{dawson_johnson_2018}, how the sizes of planets with massive
gaseous envelopes evolve \citep{rizzuto_tess_2020}, the timescales for
close-in multiplanet systems to fall out of resonance
\citep{arevalo_stability_2022,goldberg_architectures_2022}, and
whether and how mass-loss explains the radius valley
\citep{lopez_how_2012,Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018,lee_primordial_2021}.

The discovery of a young planet requires two claims to be true:
the planet must exist, and its age must be secured.  Spaced-based
photometry from K2 and TESS has yielded a number of exemplars for
which the planetary evidence comes from transits, and the age is based
on either cluster membership
\citep{Mann_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,nardiello_pathosII_2020}
or else on correlates of youth such as stellar rotation, photospheric
lithium content, x-ray activity, and emission line strength
\citep{zhou_2021_tois,hedges_toi-2076_2021}.

In this work, we leverage recent analyses of the Gaia data, which have
greatly expanded our knowledge of stellar groups \citep[{\it
e.g.},][]{CantatGaudin2018a,KounkelCovey2019,Kerr2021}.  To date these
analyses have mostly clustered on stellar positions and 2-D
velocities.  One important result has been the discovery of
diffuse streams and tidal tails comparable in stellar mass to the
previously known cores of nearby open clusters
\citep{meingast_psceri_2019,Meingast2021,gagne_number_2021}.  Even
though these streams are spread over tens to hundreds of
parsecs, their velocity dispersions can remain coherent at the
$\sim$1\kms\ level.  Internal dynamics and projection effects can also
drive them to be much larger: in the Hyades,
stars in the tidal tails are expected to span up to $\pm 40\mkms$ in velocity
relative to the cluster center \citep{jerabkova_800_2021}.
The stars in such diffuse regions can be verified to be the same age
as the core members through analyses of
color-absolute magnitude diagrams \citep{KounkelCovey2019}, stellar
rotation periods \citep{curtis_tess_2019,bouma_2021_ngc2516}, and
chemical abundances \citep{hawkins_2020}.  While there are 
implications for our understanding of star formation and cluster
evolution \citep{dinnbier_tidal_2020}, a separate consequence is that
we now know the ages of many more stars, including previously known
planet hosts.

@@

In this work, we expand on our earlier study of a $38^{+7}_{-6}$ Myr
old Neptune-sized planet in the Kepler field (Kepler-1627~Ab;
\citealt{bouma_kep1627_2022}).  This planet's age was derived
based on its host star's membership in the $\delta$\ Lyr\ cluster.
While our analysis of the cluster focused on the immediate vicinity of
Kepler-1627 in order to have a reasonable scope,  it became
clear that the $\delta$\ Lyr\ cluster seems to
also be part of a much larger group of similarly aged stars.  This
group, which is at a distance of $\sim$330\,pc from the Sun, 
spans Cepheus to Hercules (galactic longitudes, $l$, between
40$^\circ$ and 100$^\circ$), at galactic latitudes between
0$^\circ$ and 20$^\circ$.  We therefore refer to it as the Cep-Her
complex.  It exhibits significant sub-structure over its $\approx$250
parsec length, and a detailed analysis of its memberships, kinematics,
and possible origin is currently being prepared by R.~Kerr and
collaborators.

Here, our focus is on the intersection of the Cep-Her complex with the
Kepler field.  Cross-matching our Cep-Her members against known Kepler
Objects of Interest (KOIs; \citealt{thompson_planetary_2018}) yielded
four candidate cluster members: Kepler-1627, Kepler-1643, KOI-7368,
and KOI-7913.  Given our earlier analysis of Kepler-1627, we focus
here on the latter three objects.  After analyzing the relevant properties of
Cep-Her (Section~\ref{sec:cluster}), we derive the stellar properties
(Section~\ref{sec:stars}) and validate the planetary nature of each
system using a combination of the Kepler photometry and
high-resolution imaging (Section~\ref{sec:planets}).  We conclude with
a discussion of mini-Neptune size evolution, and point out possible
directions for future work (Section~\ref{sec:disc_conc}).

@@

Our focus is on a region of the Galaxy approximately 200 to 500\,pc
from the Sun, above the galactic plane, and spanning galactic
longitudes of roughly $40^\circ$ to $100^\circ$.  Two rich
clusters in this region are the $\delta$~Lyra cluster
\citep{stephenson_possible_1959} and RSG-5 \citep{roser_nine_2016}.
Each of these clusters was known before Gaia.  Their reported ages
between 30 and 60\,Myr.  Early empirical
evidence that these two clusters could be part of a large and more
diffuse population was apparent in the Gaia-based photometric analysis
of pre-main-sequence stars by \citet[][see their Figures~11
and~13]{Zari2018}.  Further kinematic connections and complexity were
highlighted by \citet{KounkelCovey2019}, who included these previously
known groups in the larger structures dubbed ``Theia~73'' and
``Theia~96''\footnote{See their visualization online at
\url{http://mkounkel.com/mw3d/mw2d.html} (accessed 15 March 2022)}.
The connection made by \citet{KounkelCovey2019} between the previously
known open clusters and the other groups in the region was made as
part of an unsupervised clustering analysis of the Gaia DR2 positions
and on-sky velocities with a subsequent manual ``stitching'' step.
Their results support the idea that there is an overdensity of
30 to 60\,Myr old stars in this region of
the Galaxy.  \citet{Kerr2021}, in a volume-limited analysis of the
Gaia DR2 point-source catalog out to one third of a kiloparsec,
identified three of the nearest sub-populations, dubbed
``Cepheus-Cygnus'', ``Lyra'', and ``Cerberus''.  \citet{Kerr2021}
reported ages for each of these subgroups between 30 and 35 Myr.

@@

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric, defined
such that the group member with the smallest core distance has a
weight of 1, the group member with the greatest core distance has a
weight of 0, and weights for the other group members are log-normally
distributed between these two extremes.  In Figure~\ref{fig:XYZvtang},
we show 12{,}436 objects with weight exceeding 0.02 as gray points,
and overplot 4{,}763 objects with weights exceeding 0.10 as black
points.\footnote{These counts only include objects with reliable
astrometry and photometry: $\varpi/\sigma_\varpi>5$;
$G/\sigma_{G}>50$; $G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm
BP}/\sigma_{G_{BP}}>20$.} The previously known $\delta$~Lyr\ cluster
is visible at $(l,b)=(68^\circ,15^\circ$) and $(v_{l'}, v_b)=(-4.5
,-4 )\mkms$.  RSG-5 is visible at $(l,b)=(83^\circ,6^\circ)$,
$(v_{l'}, v_b)=(5.5 ,-3.5 )\mkms$.  Most of the other
subclusters, including in Cep-Cyg ($l,b=90^\circ,7^\circ$) and
Cerberus ($l,b=48^\circ,18^\circ$) are too small or dispersed to have
previously been analyzed in great detail.

@@

\paragraph{Cep-Her}
Our analysis to date has focused only on portions of Cep-Her that were
observed by Kepler: RSG-5, CH-2, and the $\delta$~Lyr cluster.  The
membership and kinematics of the other subgroups shown in
Figure~\ref{fig:XYZvtang} deserve independent attention.  R.~Kerr and
collaborators have {\bf acquired N spectra} from which radial
velocities will be derived in their upcoming study, but if the
estimate that Cep-Her has $\approx$3{,}500 stars is correct then more
might be required to fully untangle the kinematics of the various
groups.  Wide-field spectroscopic surveys such as LAMOST
\citep{zhao_2012_LAMOST} or SDSS-V \citep{kollmeier_2017} could
provide sensitivity to the Li 6708\,\AA\ line, which would enable a
more detailed analysis of its abundance across the FGK members.  Gaia
DR3 may also provide RVS spectra for some of the brighter F and G
dwarfs, which would contain the calcium infrared triplet as another
age indicator.

A number of worthy photometric projects also seem possible given the
new understanding of the complex.  One is asteroseismology of the
$\delta$~Sct stars, using either TESS or Kepler data
\citep{bedding_very_2020}.  For cases in which the modes are resolved,
this might yield age estimates for subgroups independent from other
approaches.  Other projects could include searches of the Kepler light
curves for exocomets \citep{zieba_transiting_2019}, and for missed
planets around the most rapid rotators.

\paragraph{Exoplanet demographics at early times}
Our main motivation for finding new young planets is to help benchmark models
for planetary evolution.  However demographic analyses of the known planets
between $10^7$ and $10^9$ years have so far been somewhat limited.
Approximately 40 such planets are now known (Figure~\ref{fig:age}).  The
majority of published cases ($\approx$20) come from K2, though now $\approx$10
come from Kepler, and $\approx$10 from TESS.

Given the current state of the field, a few reflections regarding experimental
design of a demographic survey might be useful.  The first is that the list of
target stars with known ages is an essential ingredient.  The best way to
compile relevant stars right now is likely by combining automated
spatio-kinematic clustering from Gaia with rotation periods measured using TESS
\citep[see the appendices of][]{bouma_kep1627_2022}.  The second consideration
is that known young planets smaller than $3$\,$R_\oplus$ all come from either
K2 or Kepler.  Demographic inferences based on TESS are therefore limited to
sizes $\gtrsim4$\,$R_\oplus$, for planets close-in to their host stars.  It
seems worthwhile to compare the absolute occurrence rate of such planets to
those observed by Kepler.  One specific question that seems within reach would
be to clarify whether enough young stars have been searched for the dearth of
young hot Jupiters shown in Figure~\ref{fig:age} to be significant.  Since the
hot Jupiter occurrence rate is strongly dependent on stellar mass and
metallicity \citep{petigura_metallicity_2018,petigura_cksX_2022}, particular
care would be needed to select a sample of well-studied FGK dwarfs for the
measurement, likely including stars in Sco OB2, Cep-Her, and Orion.  For
demographic studies focused on how mini-Neptune sizes evolve, the combined K2
and Kepler dataset might be the better primary source.

@@

%\clearpage
\acknowledgements
\raggedbottom
%
L.G.B{.} acknowledges support from the TESS GI Program (NASA grants
{\bf double check 80NSSC19K0386 and 80NSSC19K1728}) and the Heising-Simons Foundation (51 Pegasi~b
Fellowship).
% programs G011103 and G022117, through 
%
%
%FIXME
Keck/NIRC2 imaging was acquired by programs
2019X
{\bf  2019A/N069 (PI: E.~Petigura)},
{\bf  20NNA/N0XX (PI: D.~Huber)}
%2015A/N301N2L (PI: A.~Kraus).
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
This paper also includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham,
S.~Seager, J.~Jenkins) and the many TESS team members for their
efforts to make the mission a continued success.
%
%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
%Finally, this research has made use of the Keck Observatory Archive (KOA),
%which is operated by the W. M. Keck Observatory and the NASA Exoplanet
%Science Institute (NExScI), under contract with the National
%Aeronautics and Space Administration.
Finally, we also thank the Keck Observatory staff for their support of
HIRES and remote observing.  We recognize the importance that the
summit of Maunakea has within the indigenous Hawaiian community, and
are deeply grateful to have the opportunity to conduct observations
from this mountain.
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%

@@

% \clearpage
\bibliographystyle{yahapj}                            
\bibliography{bibliography}

@@

%Tables~\ref{tab:kepler1643}, \ref{tab:koi7368}, \ref{tab:koi7913} give
Table~\ref{tab:kois} gives
the full set of fitted and derived parameters from the model described in
Section~\ref{sec:fitting}.
Priors and convergence statistics are also listed.

@@

\input{source_KOIs_simpletransit_posteriortable.tex}
%\input{source_Kepler_1643_simpletransit_posteriortable.tex}
%\input{source_KOI_7368_simpletransit_posteriortable.tex}
%\input{source_KOI_7913_simpletransit_posteriortable.tex}
